---
title: "Data Prep"
author: "Matthew Ross"
date: "8/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(sf)
```


## Watershed terrain metrics prep

Raw data comes from state of West Virginia (see Ross et al., 2016) or NED 
(code makes it clear which one). 

Just simplifying and cleaning the data so that it can be saved as a
fast loading .RData file for making figures and analyses. 

```{r}

## DEM FROM NED 
mud <- raster('data/rasters/mud_10m_dem')
## Lidar derived DEM
lidmud <- raster('data/rasters/DEM_5m.tif') %>% crop(.,extent(mud)) %>% projectRaster(.,mud)
mud[!is.na(lidmud)] <- lidmud[!is.na(lidmud)]
outlines <- st_read('data/shapefiles/watershedoutlines/AllWatersheds_WithVFs.shp')  %>%
  st_transform(st_crs(mud))


mud <- crop(mud,extent(outlines)) %>% crop(.,outlines) %>% mask(.,outlines)
mud.slope <- terrain(mud,opt='slope')
mud.aspect <- terrain(mud,opt='aspect')
mud.shade <- hillShade(mud.slope,mud.aspect,angle=35,270)
save(all,mud,mud.slope,mud.aspect,mud.shade,file='data/rdatas/MudRiverRast.RData')

```


## Canopy analysis prep

This paper includes an analysis of canopy height (generated from the same Lidar
data previously mentioned). Here we prepare the canopy height data for analysis.

```{r}
setwd("/media/mrr26/Extra Drive 1/Dropbox/Shared Science/NSF_MTM_All/MTM_GIS/Shapefiles")
vfs <- readOGR('Valifils/','AllVF_W_YR')


setwd("/media/mrr26/Extra Drive 1/Dropbox/My Research/MTM.VF.Age")


# cume.max <- raster("/media/mrr26/Extra Drive 1/Dropbox/Shared Science/NSF_MTM_All/MTM_GIS/Pericak_Summer16/Data/outputProducts/totalCumulativeMineArea_1014.tif")
# plot(cume.max)
# cume.max <- reclassify(cume.max,c(0,1.5,1984))
# cume.max <- reclassify(cume.max,c(-.1,1983,NA))
# cume.max[!is.na(ras.max)] <- NA
# ras.max[!is.na(cume.max)] <- 1984

#writeRaster(ras.max,'lastmine1.tif',overwrite=T)

ras.max <- raster('lastmine1.tif')
#writeRaster(ras.prj,'lastwv.tif',overwrite=T)
wv <- raster('lastwv.tif')

# forest <- raster('~/Dropbox/Shared Science/NSF_MTM_All/MTM_GIS/wvLanduseLandcover_nrac_122012_utm83_grid/wv_lulc_2011') %>%
#   projectRaster(.,ch)
#
# frst <- reclassify(forest,c(1.00001,26,NA))
# ref <- ch
# ref[is.na(frst)] <- NA
#
# writeRaster(ref,'refcanopy.tif')
canp <- raster('refcanopy.tif')

# stand.age <- raster('usgs_landcarbon/fsage_a1b_2010.tif')  %>% projectRaster(.,crs=projection(canp)) %>%
#    crop(.,canp)




# 
# 
#writeRaster(stand.age, file='studycanopyage.tif',overwrite=T)
#stand.age <- raster('studycanopyage.tif') %>% projectRaster(.,canp,method='ngb')


# canp.age <- canp %>% aggregate(.,fact=8,fun=median) %>%
#   projectRaster(.,stand.age)
# 
# wv.250 <- wv %>% aggregate(.,fact=8,fun=median,na.rm=T) %>%
#   project(raster.,stand.age)




# ch <- raster('~/Dropbox/Shared Science/NSF_MTM_All/MTM_GIS/FusionWV/DSM_5m_norm.tif') %>%
#   aggregate(.,fact=6,fun=median,na.rm=T)

#writeRaster(ch,'canopy.tif',overwrite=T)
m1 <- function(x,na.rm){
  length(x[x<1])
}

m2 <- function(x,na.rm){
  length(x[x<2])
}

# p1m.r <- raster('~/Dropbox/Shared Science/NSF_MTM_All/MTM_GIS/FusionWV/DSM_5m_norm.tif') %>%
#    aggregate(.,fact=6,fun=m1)
# 
# ref1.p <- p1m.r
# ref1.p[is.na(frst)] <- NA
# forest <- raster('~/Dropbox/Shared Science/NSF_MTM_All/MTM_GIS/wvLanduseLandcover_nrac_122012_utm83_grid/wv_lulc_2011') %>%
#   projectRaster(.,ch)
# 
# frst <- reclassify(forest,c(1.00001,26,NA))
#ref.p <- p2m.r
#ref.p[is.na(frst)] <- NA
#writeRaster(p1m.r,file='canopyagg1m.tif')
#writeRaster(ref.p,file='refgrassp.tif')
#writeRaster(ref1.p,file='ref1grassp.tif')
#writeRaster(p2m.r,'canopyagg2m.tif')
p2m.r <- raster('canopyagg2m.tif')
ref2.p <- raster('refgrassp.tif')
ref1.p <- raster('ref1grassp.tif')
p1m.r <- raster('canopyagg1m.tif')

ch <- raster('canopy.tif')
#ras.prj <- projectRaster(ras.max,ch)





# et <-  raster('MOD16A3_ET_2010.tif') %>%
# crop(.,projectExtent(ch,projection(.))) %>%
# projectRaster(.,ch)

#ndvi <- raster('greenest2010.tif',band=5) %>% crop(.,projectExtent(ch,projection(.))) %>% projectRaster(.,ch)
# blue <-   raster('greenest2010.tif',band=1) %>% crop(.,projectExtent(ch,projection(.))) %>% projectRaster(.,ch)
# green <-  raster('greenest2010.tif',band=2) %>% crop(.,projectExtent(ch,projection(.))) %>% projectRaster(.,ch)
# red <-  raster('greenest2010.tif',band=3) %>% crop(.,projectExtent(ch,projection(.))) %>% projectRaster(.,ch)
# ir <-  raster('greenest2010.tif',band=4) %>% crop(.,projectExtent(ch,projection(.))) %>% projectRaster(.,ch)

#
# vfs <- vfs %>% spTransform(.,projection(wv))
# 
# vf.ch <- crop(ch,vfs)  %>% mask(.,vfs)
# vf.mn <- crop(wv,vfs) %>% mask(.,vfs)
# vf.ndvi <- crop(ndvi,vfs) %>% mask(.,vfs)
# vf.et <- crop(et, vfs) %>% mask(.,vfs)
# vf.p2 <- crop(p2m.r,vfs) %>% mask(.,vfs)
# 
# novf.ch <- mask(ch,vfs,inverse=T)
# novf.mn <- mask(wv,vfs,inverse=T)
# novf.ndvi <- mask(ndvi,vfs,inverse=T)
# novf.et <- mask(et, vfs,inverse=T)
# novf.p2 <- mask(p2m.r,vfs,inverse=T)
# #
# vf.dat <- data.frame(canopy=as.vector(vf.ch),mined=round(as.vector(vf.mn),0),p2m=as.vector(vf.p2)) %>%
#   mutate(time.since.mining=2012-mined) %>%
#   filter(!is.na(mined)) %>%
#   mutate(type='Valley fill')
# #
# novf.dat <- data.frame(canopy=as.vector(novf.ch),mined=round(as.vector(novf.mn),0),p2m=as.vector(novf.p2)) %>%
#   mutate(time.since.mining=2012-mined) %>%
#   mutate(type='Not valley fill')
# #
# comp.dat <- rbind(novf.dat,vf.dat)

#save(comp.dat,file='vfcanopy.RData')


```

